---
title: "communications"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(forcats)
library(RColorBrewer)
```


```{r}
data_Fri <- read_csv("comm-data-Fri.csv")
```

```{r}
data_Sat<- read_csv("comm-data-Sat.csv")
```

```{r}
data_Sun <- read_csv("comm-data-Sun.csv")
```

# Friday

```{r}
external_fri <- data_Fri%>%
  filter(to == "external" | from == "external")%>%
  mutate(timeblock = hour(Timestamp))
```

### The number of external texts from each location

For every time block, Wet Land has the most texts made from. 2nd most texts made from Tundra Land 8-17 time blocks; 17-22 Entry Corridor.
```{r}
timeblock_location <- external_fri%>%
  group_by(location, timeblock)%>%
  summarize(
    num = n()
  )%>%
  arrange(desc(num))
```

*What time blocks are the most popular?*
17 is the most populated time block. That is when the shift from Tundra land to Entry Corridor happens. Most of the texts are sent afternoon.

```{r}
external_fri%>%
  group_by(timeblock)%>%
  summarize(num = n())%>%
  arrange(desc(num))
```


Are there repeating numbers that made external calls?



```{r}
repeating_numbers <- external_fri%>%
  group_by(from,timeblock, location)%>%
  summarize(
    num = n()
  )
 # arrange(from, Timestamp)
```

time series of the external texts on Friday

```{r}
ggplot(data = external_fri , aes(timeblock))+
  geom_bar(aes(timeblock, fill = location))+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "Friday: Distribution of the External Texts sent from the park",
    subtitle = "Number of external texts sent from which location in which time period"
  )
```


# Saturday


```{r}
external_sat <- data_Sat%>%
  filter(to == "external" | from == "external")%>%
  mutate(timeblock = hour(Timestamp))
```

### The number of external texts from each location
For most of the time blocks, Wet Land has the most texts made from. At time block 12, it has 838 texts made.


```{r}
timeblock_location_sat <- external_sat%>%
  group_by(location, timeblock)%>%
  summarize(
    num = n()
  )%>%
  arrange(desc(num))
```

*What time blocks are the most popular?*
12 is the most populated time block. 16 is the time when Tundra land, Entry Corridor and Wet Land take turns to  have the most texts. Texts are sent through out the day.

```{r}
external_sat%>%
  group_by(timeblock)%>%
  summarize(num = n())%>%
  arrange(desc(num))
```

Are there repeating numbers that made external calls?

```{r}
repeating_numbers_sat <- external_sat%>%
  group_by(from,timeblock, location)%>%
  summarize(
    num = n()
  )
 # arrange(from, Timestamp)
```

There were 10 texts sent from the same person, 878 on Saturday. The number of texts were sent evenly to locations: Kiddie Land, Tundra Land, Wet Land. 

time series of the external texts on Saturday
```{r}
ggplot(data = external_sat , aes(timeblock))+
  geom_bar(aes(timeblock, fill = location))+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "Saturday: Distribution of the External Texts sent from the park",
    subtitle = "Number of external texts sent from which location in which time period"
  )
```


# Sunday

```{r}
external_sun <- data_Sun%>%
  filter(to == "external" | from == "external")%>%
  mutate(timeblock = hour(Timestamp))
```

### The number of external texts from each location
Wet Land is the most dominant location which has the most texts. Time block 11 in Wet Land has the most texts sent which was 5364. This is extremely high compared to Friday and Saturday.
```{r}
timeblock_location_sun <- external_sun%>%
  group_by(location, timeblock)%>%
  summarize(
    num = n()
  )%>%
  arrange(desc(num))
```

*What time blocks are the most popular?*
11am is the most populated time block.

```{r}
external_sun%>%
  group_by(timeblock)%>%
  summarize(num = n())%>%
  arrange(desc(num))
```

Are there repeating numbers that made external calls?
878 and 436 sent the most texts.
```{r}
repeating_numbers_sun <- external_sun%>%
  group_by(from,timeblock, location)%>%
  summarize(
    num = n()
  )
 # arrange(from, Timestamp)
```


time series of the external texts on Sunday

```{r}
ggplot(data = external_sun , aes(timeblock))+
  geom_bar(aes(timeblock, fill = location))+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "Sunday: Distribution of the External Texts sent from the park",
    subtitle = "Number of external texts sent from which location in which time period"
  )
```

Most active people at 11am timeblock sending to **external numbers only**

```{r}
external_sun%>%
  filter(timeblock == 11)%>%
  group_by(from)%>%
  summarize(num_texts = n())%>%
  arrange(desc(num_texts))
```

```{r}
total_sun <- data_Sun%>%
  mutate(timeblock = hour(Timestamp))%>%
  group_by(timeblock, location)%>%
  summarize(num_texts_total = n())
```

total texts made surge at 12pm timeblock
```{r}
ggplot(data = total_sun, aes(x = timeblock, y = num_texts_total))+
  geom_col(aes(fill = location))+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "Sunday: total texts (both internal and external) distribution around time"
  )
```

total internal texts made
```{r}
data_Sun%>%
  mutate(timeblock = hour(Timestamp))%>%
  filter(to != "external")%>%
  group_by(timeblock, location)%>%
  summarize(num_texts = n())%>%
  ggplot(aes(x = timeblock, y = num_texts))+
  geom_col(aes(fill = location))+
  scale_fill_brewer(palette = "Set2")+
  labs(
    title = "Sunday: internal texts distribution in time"
  )
```

Surge in external calls at 11am -- surge in total texts, mostly internal texts at 12pm. The vandalism happened at 11am and then it was discovered by the visitors at 12pm.


most active poeple on sunday